Binocular combination in the autonomic nervous system

### 2024-05-09 manuscript.Rmd
Retrying the previous commit
Changed OSF downloads and reoriented two figures

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 56GB of storage)

@@

localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
rawdir <- 'local/rawdata/'
if (!file.exists(rawdir)){dir.create(rawdir)}   # create a local directory to store raw data
figdir <- 'Figures/'
if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
datadir <- 'local/processeddata/'
if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data

@@

# if (processdata==2){
# # if we're going to need the pre-processed files, extract from zip file
#   if (!file.exists(paste0(datadir,'P101summary.RData'))){
#    if (file.exists('resources/allprocessed.zip')){file.copy('resources/allprocessed.zip',localdir)}
#    if (!file.exists('resources/allprocessed.zip')){ 
#           osfnode <- '2qu6y'
#           osfproject <- osf_retrieve_node(osfnode)
#           osffiles <- osf_ls_files(osfproject,n_max=300)
#           fid <- which(osffiles$name=='allprocessed.zip')
#           osf_download(osffiles[fid,],localdir,progress=TRUE)
#    }
#           unzip(paste0(localdir,'allprocessed.zip'),exdir=localdir)
#           d <- dir(paste0(localdir,'allprocessed'),full.names=TRUE)
#           file.copy(d,datadir)
#   }
# }

@@

pdf(paste0(figdir,"FirstHarmonic.pdf"), bg="transparent", height = 8, width = 24)

layout(matrix(c(1,2,5,5,6,7,3,4,5,5,8,9),2,6,byrow=TRUE)) 
par(mar=c(3,6,2,1))

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)

title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Suppressive weight 1F',cex.main=2)

@@

pdf(paste0(figdir,"SecondHarmonic.pdf"), bg="transparent", height = 8, width = 24)

layout(matrix(c(1,2,5,5,6,7,3,4,5,5,8,9),2,6,byrow=TRUE)) 
par(mar=c(3,6,2,1))

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)

title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Suppressive weight 2F',cex.main=2)

@@

```{r FirstHarmonicPlots, fig.cap="Contrast response functions for pupil modualations in response to flicker at 0.5Hz (panels a-d), and 0.4Hz (panels f-i), and posterior parameter distributions for the weight of interocular suppression (panel e). Within each panel (except panel e), data points are the coherently averaged amplitudes for each condition, and error bars indicate bootstrapped 95\\% confidence intervals. Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1). In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).", fig.align="center", echo=FALSE}

@@

```{r SecondHarmonicPlots, fig.cap="Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.", fig.align="center", echo=FALSE}

>>>>

processdata <- 1 # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 56GB of storage)

@@

# all files are stored in the project directory /local/ which git is told to ignore
# create a local directory to store data and outputs
localdir <- 'local/'
if (!file.exists(localdir)){dir.create(localdir)}

# create a local directory to store raw data
rawdir <- 'local/rawdata/'
if (!file.exists(rawdir)){dir.create(rawdir)}

# create a local directory to store processed data
datadir <- 'local/processeddata/'
if (!file.exists(datadir)){dir.create(datadir)}

# create a local directory to store figures
figdir <- 'Figures/'
if (!file.exists(figdir)){dir.create(figdir)}

@@

if (processdata==2){
# if we're going to need the pre-processed files, extract from zip file
  if (!file.exists(paste0(datadir,'P301_summary.RData'))){
   if (!file.exists(paste0(localdir,'IndividualSummary.zip'))){
          osfnode <- '9ebtd'
          osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)
          fid <- which(osffiles$name=='IndividualSummary.zip')
          osf_download(osffiles[fid,],localdir,progress=TRUE)
   }
          unzip(paste0(localdir,'IndividualSummary.zip'),exdir=datadir)
  }
}

if (processdata<2){
  # if we're using the pre-processed data, check it's present and download if not
exptnames <- c('AveragedataLum.RData','AveragedataLM.RData','AveragedataS.RData','AveragedataMel.RData','included.RData')
for (f in 1:length(exptnames)){
if (!file.exists(paste0(datadir,exptnames[f]))){
  if (!exists('osffiles')){
    osfnode <- '9ebtd'
    osfproject <- osf_retrieve_node(osfnode)
    osffiles <- osf_ls_files(osfproject,n_max=300)
  }
  fid <- which(osffiles$name==exptnames[f])
  osf_download(osffiles[fid,],datadir,progress=TRUE)
}}}

if (domodelling==0){
# if we're not doing the modelling, check if the model outputs are present and download if not
  exptnames <- c('modeloutputLum.RData','modeloutputLM.RData','modeloutputS.RData','modeloutputMel.RData')

for (f in 1:length(exptnames)){
if (!file.exists(paste0(datadir,exptnames[f]))){
  if (!exists('osffiles')){
    osfnode <- '9ebtd'
    osfproject <- osf_retrieve_node(osfnode)
    osffiles <- osf_ls_files(osfproject,n_max=300)
  }
  fid <- which(osffiles$name==exptnames[f])
  osf_download(osffiles[fid,],datadir,progress=TRUE)
}
}
}

@@

pdf(paste0(figdir,"FirstHarmonic.pdf"), bg="transparent", height = 24, width = 8)

layout(matrix(c(1,2,3,4,5,5,5,5,6,7,8,9),6,2,byrow=TRUE)) 
par(mar=c(3,6,2,1))

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=1, cex=1.5)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)

title(xlab=expression(omega), col.lab=rgb(0,0,0), line=4, cex.lab=6)    
title(ylab="Probability", col.lab=rgb(0,0,0), line=3, cex.lab=3)
title(main='Suppressive weight 1F',cex.main=3)

@@

pdf(paste0(figdir,"SecondHarmonic.pdf"), bg="transparent", height = 24, width = 8)

layout(matrix(c(1,2,3,4,5,5,5,5,6,7,8,9),6,2,byrow=TRUE)) 
par(mar=c(3,6,2,1))

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=1, cex=1.5)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)

title(xlab=expression(omega), col.lab=rgb(0,0,0), line=4, cex.lab=6)    
title(ylab="Probability", col.lab=rgb(0,0,0), line=3, cex.lab=3)
title(main='Suppressive weight 2F',cex.main=3)

@@

```{r FirstHarmonicPlots, fig.cap="Contrast response functions for pupil modualations in response to flicker at 0.5Hz (panels a-d), and 0.4Hz (panels f-i), and posterior parameter distributions for the weight of interocular suppression (panel e). Within each panel (except panel e), data points are the coherently averaged amplitudes for each condition, and error bars indicate bootstrapped 95\\% confidence intervals. Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1). In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).", fig.align="center", out.width="40%", echo=FALSE}

@@

```{r SecondHarmonicPlots, fig.cap="Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.", fig.align="center", out.width="40%", echo=FALSE}
